TODO

### 2021-07-01 Documents/TODO.Rmd
bayes factor first trial

- [X] Marginal densities of a multivariate normal distribution are obtained simply dropping irreleevantt variables ([link math-stackexchange](https://math.stackexchange.com/questions/2528201/find-the-marginal-distributions-pdfs-of-a-multivariate-normal-distribution)

>>>>

- [X] Marginal densities of a multivariate normal distribution are obtained simply dropping irreleevantt variables ([link math-stackexchange](https://math.stackexchange.com/questions/2528201/find-the-marginal-distributions-pdfs-of-a-multivariate-normal-distribution))
